Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Changed intro sections further.

Unfortunately, while the fairness policy used by Mesos is efficient and
strategy-proof in a simple one-shot game with homogeneous resources, it is
neither efficient nor strategy-proof in this more realistic setting. 
%For example, a framework
%using Mesos which prefers to run tasks on machines that already have relevant
%data is forced to engage in strategic behavior: given a resource which it
%\emph{could} use now, should it take the resource or decline it, so that it
%might receive a better offer in the future? Solutions to this problem rely on
%simple heuristics which require tuning based on the parameters of the system;
%there are simple examples where the resulting allocations are not efficient
%despite best-efforts of the clients, and in complex examples there is little to
%believe the results are efficient. 
Moreover, the
current design of Mesos is essentially unsuitable for hostile
environments. Section \ref{sec:theory} provides detailed theoretical analyses.
%; a framework which can use less than its ``fair share'' of the
%resources at any point in time has no incentive to do so, and indeed has every
%incentive to exploit all resources it can be allocated even if they are being
%used arbitrarily inefficiently (and there is always \emph{something} to do with
%idle resources, if only perform proof-of-work in exchange for small amounts of
%money).

@@

@@

\section{Our auction}

@@

>>>>

Unfortunately, while the fairness policy used by Mesos is efficient and
strategy-proof in a simple one-shot game with homogeneous resources, it is
neither efficient nor strategy-proof in this more realistic setting. 
For example, a framework
using Mesos which prefers to run tasks on machines that already have relevant
data is forced to engage in strategic behavior: given a resource which it
\emph{could} use now, should it take the resource or decline it, so that it
might receive a better offer in the future? Solutions to this problem rely on
simple heuristics which require tuning based on the parameters of the system;
there are simple examples where the resulting allocations are not efficient
despite best-efforts of the clients, and in complex examples there is little to
believe the results are efficient. 
Moreover, the
current design of Mesos is essentially unsuitable for hostile
environments. 
For example,
a framework which can use less than its ``fair share'' of the
resources at any point in time has no incentive to do so, and indeed has every
incentive to exploit all resources it can be allocated even if they are being
used arbitrarily inefficiently (and there is always \emph{something} to do with
idle resources, if only perform proof-of-work in exchange for small amounts of
money).
Our economic mechanisms are designed to partially remedy these problems.

@@

\subsection{Motivating examples}

Consider the following typical situations within a cluster:
\begin{enumerate}
  \item Some clients have regular throughput and flexible deadlines, while some
    clients have hard real-time constraints and variable traffic.
  \item Different tasks make use of different characteristics of hardware on
    machines in the cluster, for example high ratios of RAM to CPU on a
    particular machine, or GPUs or other hardware that is available on only
    certain machines.
  \item Tasks require data which is located on disk or even in memory somewhere
    in the cluster, and co-locating the tasks with the data improves
    performance.
\end{enumerate}

In section~\ref{drawbacks} we show that current implementations
of Mesos do not remain efficient, strategy-proof, envy-free,
or compatible with the sharing incentive under these conditions.
The key problem is that the accept/reject framework is not sufficiently expressive
to allow users to ``honestly'' express their preferences in these cases,
and so it is unsurprising that they are incentivized to engage
in strategic behavior (indeed, they are intended to engage in strategic behavior)
and the results need not be efficient.

There have bene many ad hoc proposals to address some of these difficulties.
For example, Jockey is a system which accomodates deadlines in a fair-share
scheduler by increasing the allotted shares for users which are appraoching
a deadline.
However, these techniques tend to violate the theoretical guarantees
of the underlying systems more starkly, and to require extensive tuning
in order to achieve good performance.
We seek a more general framework for addressing these difficulties.

Similarly, we might cope with the need for pre-emption by using various
heuristics to minimize the extent of overhead associated with evicting a running
task.
These heuristics may work well in practice, but are also likely to require
tuning and to be sensitive to the exact nature of the cluster.

An approach based on pricing might be able to solve all of these difficulties,
by expressing the costs associated with missing a deadline or evicting a task 
(potentially automatically) and then making scheduling decisions to maximize
social welfare.
We do not propose such an extensive solution in this paper; instead,
we make an argument for the general desirability of such an approach and provide
some extremely preliminary evidence for its feasibility.

@@

\section{Our allocation policy}

@@

In the case of a single indivisible resource, this corresponds exactly
to a second-price auction; in general it is quite similar
to the Vickrey-Clarke-Groves auction, in which the chosen allocation
maximizes social welfare and each framework is charged a price
equal to the social welfare opportunity cost of the resources
that framework requested. In the rest of this section we describe the auction
itself in more detail.
